### 2016-06-25 sec1_introduction.tex
A new draft
Flighting
Need to add three more experiments
Three more charts

\begin{figure}[h]
\centering
\includegraphics[width=0.45\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. Objects in spatial clusters are enclosed by dotted circles. $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
\label{fig:related_work}
\end{figure}

Figure~\ref{fig:related_work} is an example to demonstrate the concepts of various co-movement patterns. The trajectory database consists of six moving objects and the temporal dimension is discretized into six snapshots. In each snapshot, we treat the clustering methods as a black-box and assume that they generate the same clusters. Objects in proximity are grouped in the dotted circles. As aforementioned, there are three parameters to determine the co-movement patterns and the default settings in this example are $M=2$, $K=3$ and $L=2$. Both the \emph{flock} and the \emph{convoy} require the spatial clusters to last for at least $K$ consecutive  timestamps. Hence,$\{o_3,o_4\}$ and $\{o_5,o_6\}$  remains the only two candidates matching the patterns. The \textit{swarm} relaxes the pattern matching by discarding the temporal consecutiveness constraint. Thus, it generates many more candidates than the \textit{flock} and the \textit{convoy}. The \textit{group} and the \textit{platoon} add another constraint on local consecutiveness to retain meaningful patterns. For instance, $\{o_1,o_2:1,2,4,5\}$ is a pattern matching local consecutiveness because timestamps $\{1,2\}$ and $\{4,5\}$ are two segments with length no smaller than $L=2$. The difference between the \textit{group} and the \textit{platoon} is that the \textit{platoon} has an additional parameter $K$ to specify the minimum number of snapshots for the spatial clusters. This explains why $\{o_3,o_4,o_5:2,3\}$ is a  \textit{group} pattern but not a \textit{platoon} pattern.

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. In addition, despite the generality of the \emph{platoon} (i.e., it can be reduced to other types of patterns via proper parameter settings), it suffers from the so-called \emph{loose-connection} anomaly. We use two objects $o_1$ and $o_2$ in Figure~\ref{fig:platoon_weakpoint} as an example to illustrate the scenario. These two objects form a \emph{platoon} pattern in timestamps $\{1,2,3,102,103,104\}$. However, the two consecutive segments are $98$ timestamps apart, resulting in a false positive co-movement pattern. In reality, such an anomaly may be caused  by the periodic movements of unrelated objects, such as vehicles stopping at the same petrol station or animals pausing at the same water source. 
Unfortunately, none of the existing patterns have directly addressed this anomaly.

@@

\begin{figure}[h]
\center
\includegraphics[width=0.35\textwidth]{platoon_weakpoint.eps}
\caption{\emph{Loose-connection} anomaly. Even though $\{o_1, o_2: 1,2,3,102,103,104\}$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart. 
% in \emph{platoon}, \emph{swarm} and \emph{group} results.
}
\label{fig:platoon_weakpoint}
\end{figure}

@@

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions 
temporal points. 
The results show that both our parallel scheme efficiently supports GCMP mining in large datasets.
In particular, with near 200 million trajectory points, 
SPARE runs in 15 minutes using 172 cores. Whereas
centralized solutions take near 7 hours 
for 1 million trajectory points.
Moreover, our optimized SPARE methods achieves upto 10 times efficiency
as compared to the baseline algorithm with almost linear scalability.

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=0.46\textwidth]{related_work.eps}
\caption{Trajectories and co-movement patterns; The example consists of six trajectories across six snapshots. Objects in spatial clusters are enclosed by dotted circles. $M$ is the minimum cluster cardinality; $K$ denotes the minimum number of snapshots for the occurrence of a spatial cluster; and $L$ denotes the minimum length for local consecutiveness.}
\label{fig:related_work}
\end{figure}

Figure~\ref{fig:related_work} is an example to demonstrate the concepts of various co-movement patterns. The trajectory database consists of six moving objects and the temporal dimension is discretized into six snapshots. In each snapshot, we treat the clustering methods as a black-box and assume that they generate the same clusters. Objects in proximity are grouped in the dotted circles. As aforementioned, there are three parameters to determine the co-movement patterns and the default settings in this example are $M=2$, $K=3$ and $L=2$. Both the \emph{flock} and the \emph{convoy} require the spatial clusters to last for at least $K$ consecutive  timestamps. Hence,$\langle o_3,o_4:1,2,3 \rangle$ and $\langle o_5,o_6:3,4,5 \rangle$  remains the only two candidates matching the patterns. The \textit{swarm} relaxes the pattern matching by discarding the temporal consecutiveness constraint. Thus, it generates many more candidates than the \textit{flock} and the \textit{convoy}. The \textit{group} and the \textit{platoon} add another constraint on local consecutiveness to retain meaningful patterns. For instance, $\langle o_1,o_2:1,2,4,5 \rangle$ is a pattern matching local consecutiveness because timestamps $(1,2)$ and $(4,5)$ are two segments with length no smaller than $L=2$. The difference between the \textit{group} and the \textit{platoon} is that the \textit{platoon} has an additional parameter $K$ to specify the minimum number of snapshots for the spatial clusters. This explains why $\langle o_3,o_4,o_5:2,3 \rangle$ is a  \textit{group} pattern but not a \textit{platoon} pattern.

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. In addition, despite the generality of the \emph{platoon} (i.e., it can be reduced to other types of patterns via proper parameter settings), it suffers from the so-called \emph{loose-connection} anomaly. We use two objects $o_1$ and $o_2$ in Figure~\ref{fig:platoon_weakpoint} as an example to illustrate the scenario. These two objects form a \emph{platoon} pattern in timestamps $(1,2,3,102,103,104)$. However, the two consecutive segments are $98$ timestamps apart, resulting in a false positive co-movement pattern. In reality, such an anomaly may be caused  by the periodic movements of unrelated objects, such as vehicles stopping at the same petrol station or animals pausing at the same water source. 
Unfortunately, none of the existing patterns have directly addressed this anomaly.

@@

\begin{figure}[h]
\center
\includegraphics[width=0.35\textwidth]{platoon_weakpoint.eps}
\caption{\emph{Loose-connection} anomaly. Even though $\langle o_1, o_2: 1,2,3,102,103,104 \rangle$ is considered as a valid \emph{platoon} pattern, it is highly probable that these two objects are not related as the two consecutive segments  are 98 timestamps apart. 
% in \emph{platoon}, \emph{swarm} and \emph{group} results.
}
\label{fig:platoon_weakpoint}
\end{figure}

@@

We conduct a set of extensive experiments on three large-scaled real datasets with hundreds of millions 
temporal points. 
The results show that both our parallel scheme efficiently supports GCMP mining in large datasets.
In particular, with near 200 million trajectory points, 
SPARE runs in 15 minutes using 162 cores. Whereas
centralized solutions take near 7 hours 
for 1 million trajectory points.
Moreover, our optimized SPARE methods achieves upto 10 times efficiency
as compared to the baseline algorithm with almost linear scalability.

### 2016-06-25 sec4_baseline.tex
Need to add three more experiments
Three more charts

\section{Baseline: Temporal Replication and Parallel Mining}
\label{sec:trm}
In this section, we propose a baseline solution that resorts to MapReduce (MR) as a general, parallel and scalable paradigm for GCMP pattern mining. The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}. There are two cycles of map-reduce jobs connected in a pipeline manner. The first cycle deals with spatial clustering in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining. In particular, the timestamp is treated as the key in the map phase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phase. Finally, the reducers output clusters of objects in each snapshot, represented by a list of $\langle t,S_t \rangle$ pairs, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.

@@

Details of the algorithm are presented in Algorithm~\ref{algo:line-sweep}. We keep a candidate set $C$ (Line~\ref{code:ls-can-set}) during the sweeping process. It is initialized as the candidate clusters with size no smaller than $M$ in the first snapshot. Then, we sequentially scan each snapshot (Lines~\ref{code:ls-sweep-starts}-\ref{code:ls-sweep-ends}) and generate new candidates by extending the original ones in $C$.
In particular, we join candidates in $C$ with all the clusters in $S_j$ to form new candidates (Lines~\ref{code:ls-join-start}-\ref{code:ls-join-ends}). 
%The join of candidate $c$ and cluster $s$ creates a
%new candidate $c'$ (Line~\ref{code:ls-join}).  
After sweeping all the snapshots, all the valid patterns are stored in $C$(Line~\ref{code:ls-valid-check}). 
It is worth noting that $C$ continues to grow during the whole sweeping process. We can use three pruning rules to 
early remove false candidates from $C$. Since there is a partition $\lambda_t$ for each $S_t$, 
in line sweep, only patterns that starts from timestamp $t$ (i.e., $S_t$) need to be discovered. Therefore, those patterns that does not appear in the $S_t$ are false candidates. Particularly, our
three pruning rules are as follows:
First, when sweeping snapshot $S_j$, new candidates with objects set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joined with all clusters in $S_j$, 
candidates in $C$ with the maximum timestamp no greater than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}). Third, candidates in $C$ with the size of first segment smaller than $L$
are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ could be significantly reduced.

@@

The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}. We illustrate the workflow of TRPM method using Figure~\ref{fig:trm} (c)(d) with pattern
parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+2K - 2 = 5$. Therefore, 
in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set
during sweeping snapshot $S_i$.
Initially, $C_1$ contains patterns with object sets in snapshot $S_1$.
As we sweep the snapshots, the patterns in $C_i$ grow. At snapshot $S_4$, the candidate
$\{o_5,o_6\}$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
and the next scanning timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
Next, at snapshot $S_5$, the candidate $\{o_1,o_2\}$ is removed. This is
because its local consecutive segment $\{4\}$ has only $1$ element,
which violates the $L$-consecutive constraint.
Finally, $\{o_3,o_4\}$ is the valid pattern and is returned. Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness. If $\eta$ is set to $4$, the pattern $\{o_3,o_4\}$ would be missed.

>>>>

\section{Baseline: Temporal Replication and Parallel Mining}
\label{sec:trm}
In this section, we propose a baseline solution that resorts to MapReduce (MR) as a general, parallel and scalable paradigm for GCMP pattern mining. The framework, named \textit{temporal replication and parallel mining} (TRPM), is illustrated in   Figure~\ref{fig:trm}. There are two cycles of map-reduce jobs connected in a pipeline manner. The first cycle deals with spatial clustering in each snapshot, which can be seen as a preprocessing step for the subsequent pattern mining. In particular, the timestamp is treated as the key in the map phase and objects within the same snapshot are clustered (DBSCAN or disk-based clustering) in the reduce phase. Finally, the reducers output clusters of objects in each snapshot, represented by a list of key-value pairs $\langle t, S_t  \rangle$, where $t$ is the timestamp and $S_t$ is a set of clustered objects at snapshot $t$.

@@

Details of the algorithm are presented in Algorithm~\ref{algo:line-sweep}. We keep a candidate set $C$ (Line~\ref{code:ls-can-set}) during the sweeping process. It is initialized as the candidate clusters with size no smaller than $M$ in the first snapshot. Then, we sequentially scan each snapshot (Lines~\ref{code:ls-sweep-starts}-\ref{code:ls-sweep-ends}) and generate new candidates by extending the original ones in $C$.
In particular, we join candidates in $C$ with all the clusters in $S_j$ to form new candidates (Lines~\ref{code:ls-join-start}-\ref{code:ls-join-ends}). 
%The join of candidate $c$ and cluster $s$ creates a
%new candidate $c'$ (Line~\ref{code:ls-join}).  
After sweeping all the snapshots, all the valid patterns are stored in $C$(Line~\ref{code:ls-valid-check}). 
It is worth noting that $C$ continues to grow during the whole sweeping process. We can use three pruning rules to 
early remove false candidates from $C$. Since there is a partition $\lambda_t$ for each $S_t$, only patterns that start from timestamp $t$ need to be discovered. Therefore, those patterns that does not appear in the $S_t$ are false candidates. Particularly, our
three pruning rules are as follows:
First, when sweeping snapshot $S_j$, new candidates with objects set smaller than $M$ are pruned (Line~\ref{code:ls-m-prun}). Second, after joined with all clusters in $S_j$, 
candidates in $C$ with the maximum timestamp no greater than $j-G$ are pruned (Lines~\ref{code:ls-g-prune-starts}-\ref{code:ls-g-prune-ends}). Third, candidates in $C$ with the size of first segment smaller than $L$
are pruned (Lines~\ref{code:ls-l-prune-starts}-\ref{code:ls-l-prune-ends}). With the three pruning rules, the size of $C$ could be significantly reduced.

@@

The complete picture of temporal replication and parallel mining is summarized in Algorithm~\ref{algo:trm_overview}. We illustrate the workflow of TRPM method using Figure~\ref{fig:trm} (c)(d) with pattern
parameters $M=2, K=3, L = 2, G=2$. By Theorem~\ref{THM:RP_ETA}, $\eta$ is calculated
as $(\lceil \frac{K}{L} \rceil-1) *(G-1)+2K - 2 = 5$. Therefore, 
in Figure~\ref{fig:trm} (c), every $5$ consecutive snapshots are combined 
into a partition in the map phase. In Figure~\ref{fig:trm} (d), a line sweep
method is illustrated for partition $\lambda_1$. Let $C_i$ be the candidate set
during sweeping snapshot $S_i$.
Initially, $C_1$ contains patterns with object sets in snapshot $S_1$.
As we sweep the snapshots, the patterns in $C_i$ grow. At snapshot $S_4$, the candidate
$\langle o_5,o_6 \rangle$ is removed. This is because the gap between its latest timestamp (i.e., $2$)
and the next scanning timestamp (i.e., $5$) is $3$, which violates the $G$-connected constraint.
Next, at snapshot $S_5$, the candidate $\langle o_1,o_2 \rangle$ is removed. This is
because its local consecutive segment $(4)$ has only $1$ element,
which violates the $L$-consecutive constraint.
Finally, $\langle o_3,o_4 \rangle$ is the valid pattern and is returned. Note that in this example, $\eta=5$ is the minimum setting that can guarantee correctness. If $\eta$ is set to $4$, the pattern $\langle o_3,o_4 \rangle$ would be missed.

### 2016-06-25 sec5_spm.tex
Need to add three more experiments
Three more charts

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks. First, the replication relies on $\eta$ which could be large. Second, the same valid pattern may be discovered from different partitions which results in redundant works.
%and results in groups of snapshots in each partition.
% ADD MORE DETAILS ABOUT THE LIMITATIONS HERE.
To resolve the limitations caused by the replicate partitioning, 
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

\subsection{Star Partitioning}
Let $G_t$ be a graph for snapshot $S_t$, in which each node 
is a moving object and two objects are connected if they appear 
in the same cluster. It is obvious that $G_t$ consists of a set of small cliques. 
Based on $G_t$, we define an aggregated graph $G_A$ to summarize the 
cluster relationship among all the snapshots. In $G_A$, two objects
form an edge if they are connected in any $G_t$s. Furthermore, 
we attach an inverted list for each edge, 
storing the associated timestamps in which the two objects are connected. 
An example of $G_A$, built on the trajectory database in Figure~\ref{fig:related_work}, 
is shown in Figure~\ref{fig:star_partition} (a). 
As long as two objects are clustered in any timestamp, they are connected in $G_A$. 
The object pair $(o_1,o_2)$ appears in two clusters at timestamps 
$2$ and $3$ and is thus associated with an inverted list $\{2,3\}$.

@@

\begin{theorem}
\label{THM:SPM_LB}
Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be value derived from a random vertex ordering. With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}
\begin{proof}
In Appendix XXX.
\end{proof}
If $G_A$ is a dense graph, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
\begin{theorem}
\label{THM:SPM_LB_INC}
Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
\end{theorem}
\begin{proof}
In Appendix XXXX.
\end{proof}
Hence, we can simply use object id to determine the vertex ordering in our implementation.

%
%Even though the TRM algorithm works in a parallel way, it requires to replicate the data $\eta$ times. 
%When $\eta$ is small, TRM perform good parallelism. However, wh
%
%When handling \emph{swarm}, \emph{group} and \emph{platoon} patterns, $\eta$ has to be set to $|\mathbb{T}|$ to guarantee correctness, resulting in very expensive data replication overhead. 
%%Handling those cases are equivalent to replicate the entire snapshots to each partition, 
%%which surrenders the benefit of parallelism.
\eat{
Although TRPM works in a parallel way, we observe two inefficiencies. First, the
performance of TRPM largely relies on $\eta$ which further depends on pattern parameters.
When $\eta$ is large, the shuffle and reduce cost of TRPM is high. Second, 
the parallel execution of line sweep algorithm may discover the same pattern from
multiple partitions, which introduces redundant work. To resolve the two limitations,
we design a novel \emph{Star Partition and Mining} algorithm.
}
%After computing the star, each partition is applied with a reduce task. 
%Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. 
%This is done by treating each vertex in $Sr_s$ as an object. 
%The time sequence of $s$ is the union of all edges in $Sr_s$. 
%And the time sequence of $v \neq s$ is the edge $(s,v)$. Therefore, we
%are able to mine stars from the similar trajectory concepts.

\subsection{Apriori Enumerator}
Intuitively, given a GCMP pattern with an object set $\{o_1,o_2,\ldots,o_m\}$, 
all the pairs of $(o_i,o_j)$ with $1\leq i<j\leq m$ must 
be connected in the associated temporal graphs $\{G_t\}$. This inspires us to leverage the classic Apriori algorithm to enumerate all the valid GCMP patterns starting from pairs of objects. However, we observe that the monotonicity property does not hold between an object set and its supersets.

\begin{example}
In this example, we show that if an object set is not a valid pattern, we cannot prune all its super sets.
Consider two candidates $P_1=\{o_1,o_2:1,2,3,6\}$ and $P_2=\{o_1,o_3:1,2,3,7\}$. 
Let $L=2,K=3$ and $G=2$. Both candidates are not valid patterns because the constraint on $L$ is not satisfied. 
However, when considering their object superset $\{o_1,o_2,o_3\}$, we can infer that their co-clustering timestamps are in $(1,2,3)$. This is a valid pattern conforming to the constraints of $L,K,G$. Thus, we need a new type of monotonicity to facilitate pruning.
\end{example}

@@

\begin{algorithm}
\caption{Apriori Enumerator}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$C \leftarrow \emptyset$}
\ForAll{edges $c=\langle o_i\cup o_j, T_{o_i}\cap T_{o_j}\rangle$ in $Sr_s$} \label{code:init-start}
\If {$\mathtt{sim}(T_{o_i}\cap T_{o_j})\neq \emptyset$}
\State {$C\leftarrow C\cup \{c\}$} \label{code:simp1}
%\ElsIf{$c$ is a valid pattern}
%\State{output $c$}
\EndIf 
\EndFor\label{code:init-end}
\State $\mathrm{level} \gets 2$ \label{code:level}
\While{$C\neq \emptyset$} \label{code:level-start}
	\ForAll{$c_1 \in C$}
		\ForAll{$c_2 \in C$ and $|c_2.O \cup c_2.O| = \mathrm{level}$}\label{code:join-start}	
			\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}			
			\If{ $\mathtt{sim}(c'.T)\neq \emptyset$} \label{code:simp2}
					\State {$C'\leftarrow C'\cup \{c'\}$}
			\EndIf			
		\EndFor\label{code:join-end}
		\If {no $c'$ is added to $C'$} \label{code:output1-start}
			\If{$c_1$ is a valid pattern}
				\State output $c_1$
			\EndIf
		\EndIf \label{code:output1-end}
	\EndFor
%	
%		\ForAll{pairs $c_1\in C$, $c_2\in C$ and $c_1\neq c_2$} \label{code:join-start}
%				\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}
%				\If{ $\mathtt{sim}(c_1.T \cap c_2.T )\neq \emptyset$}
%					\State {$C'\leftarrow C'\cup \{c'\}$}
%					\ElsIf{$c'$ is a valid pattern}
%						\State{output $c'$}
%				\EndIf
%		\EndFor	\label{code:join-ends}
	\State $O_u \gets $ union of $c.O$ in $C$	\label{code:fc-checking-start}
	\State $T_u \gets $ intersection of $c.T$ in $C$	
	\If {$\langle O_u, T_u\rangle$ is a valid pattern}
		\State{output $\langle O_u, T_u\rangle$} \label{code:fc-checking}
		\State break;
	\EndIf \label{code:fc-checking-end}
	\State {$C\leftarrow C';C'\leftarrow \emptyset; \mathrm{level} \gets \mathrm{level}+1$}	
\EndWhile\label{code:level-ends}
\State output $C$ \label{code:output2-end}
\end{algorithmic}
\end{algorithm}

\begin{example}
As shown in Figure~\ref{fig:star_partition}(c), in the bottom level of the lattice structure, candidate $\{3,6:3\}$ is pruned because its simplified sequence is empty. Thus, all the object sets containing $\{3,6\}$ can be pruned. The remaining two candidates (i.e., $\{3,4:1,2,3\}$ and $\{3,5:2,3\}$)  derive a new  $\{3,4,5:2,3\}$ which is valid. By the forward closure checking, the algorithm can terminate and output $\{3,4,5:2,3\}$ as the final closed pattern.
\end{example}

\subsection{Put It Together}
We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, for ease of presentation, we used an aggregated graph $G_A$ to capture the clustering relationship. However, in the implementation of the map phrase, there is no need to create $G_A$ in advance.  Instead, we simply need to emit the edges within a star partition to the same reducer.  Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a candidate pattern $\{o,i: e(o,i)\}$ is created. Then it enumerates all the valid patterns from the candidate patterns. The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.

@@

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we prove the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
See Appendix XXXX.
\end{proof}

>>>>

\section{SPARE: Star Partitioning and Apriori Enumerator}
\label{sec:spm}
The aforementioned replicate partitioning is based on the temporal dimension which suffers from two drawbacks. First, the replication relies on $\eta$ which could be large. Second, the same valid pattern may be discovered from different partitions which results in redundant works.
To resolve the limitations caused by the replicate partitioning, 
we propose a new Star Partitioning and ApRiori Enumerator, named SPARE, 
to replace the second cycle of map-reduce jobs in Figure~\ref{fig:trm}. 
Our new parallel mining framework is shown in Figure~\ref{fig:star_partition}. 
Its input is the set of clusters generated in each snapshot and the output 
contains all the valid GCMP patterns. In the following, we explain the two major components: 
star partitioning and apriori enumerator.

\subsection{Star Partitioning}
Let $G_t$ be a graph for snapshot $S_t$, in which each node 
is a moving object and two objects are connected if they appear 
in the same cluster. It is obvious that $G_t$ consists of a set of small cliques. 
Based on $G_t$, we define an aggregated graph $G_A$ to summarize the 
cluster relationship among all the snapshots. In $G_A$, two objects
form an edge if they are connected in any $G_t$s. Furthermore, 
we attach an inverted list for each edge, 
storing the associated timestamps in which the two objects are connected. 
An example of $G_A$, built on the trajectory database in Figure~\ref{fig:related_work}, 
is shown in Figure~\ref{fig:star_partition} (a). 
As long as two objects are clustered in any timestamps, they are connected in $G_A$. 
The object pair $\langle o_1,o_2 \rangle$ appears in two clusters at timestamps 
$2$ and $3$ and is thus associated with an inverted list $(2,3)$.

@@

\begin{theorem}
\label{THM:SPM_LB}
Let $\Gamma^*$ be the value derived from the optimal vertex ordering and  $\Gamma$ be value derived from a random vertex ordering. With probability $1-1/n$, we have $\Gamma = \Gamma^* + O(\sqrt{n \log n})$.
\end{theorem}
\begin{proof}
In Appendix~\ref{apx:thm2proof}.
\end{proof}
If $G_A$ is a dense graph, we can get a tighter bound for $(\Gamma - \Gamma^*)$.
\begin{theorem}
\label{THM:SPM_LB_INC}
Let $d$ be the average degree in $G_A$. If $d\geq \sqrt{12\log n}$, with
high probability $1-1/n$, $\Gamma = \Gamma^* + O(\sqrt{d\log n})$.
\end{theorem}
\begin{proof}
In Appendix~\ref{apx:thm2proof}.
\end{proof}
Hence, we can simply use object id to determine the vertex ordering in our implementation.

%
%Even though the TRM algorithm works in a parallel way, it requires to replicate the data $\eta$ times. 
%When $\eta$ is small, TRM perform good parallelism. However, wh
%
%When handling \emph{swarm}, \emph{group} and \emph{platoon} patterns, $\eta$ has to be set to $|\mathbb{T}|$ to guarantee correctness, resulting in very expensive data replication overhead. 
%%Handling those cases are equivalent to replicate the entire snapshots to each partition, 
%%which surrenders the benefit of parallelism.
%\eat{
%Although TRPM works in a parallel way, we observe two inefficiencies. First, the
%performance of TRPM largely relies on $\eta$ which further depends on pattern parameters.
%When $\eta$ is large, the shuffle and reduce cost of TRPM is high. Second, 
%the parallel execution of line sweep algorithm may discover the same pattern from
%multiple partitions, which introduces redundant work. To resolve the two limitations,
%we design a novel \emph{Star Partition and Mining} algorithm.
%}
%After computing the star, each partition is applied with a reduce task. 
%Indeed, a star $Sr_s$ can be viewed as a subset of original trajectories. 
%This is done by treating each vertex in $Sr_s$ as an object. 
%The time sequence of $s$ is the union of all edges in $Sr_s$. 
%And the time sequence of $v \neq s$ is the edge $(s,v)$. Therefore, we
%are able to mine stars from the similar trajectory concepts.

\subsection{Apriori Enumerator}
Intuitively, given a GCMP pattern with an object set $\{o_1,o_2,\ldots,o_m\}$, 
all the pairs of $\langle o_i,o_j \rangle$ with $1\leq i<j\leq m$ must 
be connected in the associated temporal graphs $\{G_t\}$. This inspires us to leverage the classic Apriori algorithm to enumerate all the valid GCMP patterns starting from pairs of objects. However, we observe that the monotonicity property does not hold between an object set and its supersets.

\begin{example}
In this example, we show that if an object set is not a valid pattern, we cannot prune all its super sets.
Consider two candidates $P_1=\langle o_1,o_2:1,2,3,6 \rangle$ and $P_2=\langle o_1,o_3:1,2,3,7 \rangle$. 
Let $L=2,K=3$ and $G=2$. Both candidates are not valid patterns because the constraint on $L$ is not satisfied. 
However, when considering their object superset $\langle o_1,o_2,o_3 \rangle$, we can infer that their co-clustering timestamps are in $(1,2,3)$. This is a valid pattern conforming to the constraints of $L,K,G$. Thus, we need a new type of monotonicity to facilitate pruning.
\end{example}

@@

\begin{algorithm}[h]
\caption{Apriori Enumerator}
\label{algo:apriori_mining}
\begin{algorithmic}[1]
\Require{$Sr_s$}
\State {$C \leftarrow \emptyset$}
\ForAll{edges $c=\langle o_i\cup o_j, T_{o_i}\cap T_{o_j}\rangle$ in $Sr_s$} \label{code:init-start}
\If {$\mathtt{sim}(T_{o_i}\cap T_{o_j})\neq \emptyset$}
\State {$C\leftarrow C\cup \{c\}$} \label{code:simp1}
%\ElsIf{$c$ is a valid pattern}
%\State{output $c$}
\EndIf 
\EndFor\label{code:init-end}
\State $\mathrm{level} \gets 2$ \label{code:level}
\While{$C\neq \emptyset$} \label{code:level-start}
	\ForAll{$c_1 \in C$}
		\ForAll{$c_2 \in C$ and $|c_2.O \cup c_2.O| = \mathrm{level}$}\label{code:join-start}	
			\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}			
			\If{ $\mathtt{sim}(c'.T)\neq \emptyset$} \label{code:simp2}
					\State {$C'\leftarrow C'\cup \{c'\}$}
			\EndIf			
		\EndFor\label{code:join-end}
		\If {no $c'$ is added to $C'$} \label{code:output1-start}
			\If{$c_1$ is a valid pattern}
				\State output $c_1$
			\EndIf
		\EndIf \label{code:output1-end}
	\EndFor
%	
%		\ForAll{pairs $c_1\in C$, $c_2\in C$ and $c_1\neq c_2$} \label{code:join-start}
%				\State {$c' \gets \langle c_1.O \cup c_2.O:(c_1.T \cap c_2.T )\rangle$} \label{code:join}
%				\If{ $\mathtt{sim}(c_1.T \cap c_2.T )\neq \emptyset$}
%					\State {$C'\leftarrow C'\cup \{c'\}$}
%					\ElsIf{$c'$ is a valid pattern}
%						\State{output $c'$}
%				\EndIf
%		\EndFor	\label{code:join-ends}
	\State $O_u \gets $ union of $c.O$ in $C$	\label{code:fc-checking-start}
	\State $T_u \gets $ intersection of $c.T$ in $C$	
	\If {$\langle O_u, T_u\rangle$ is a valid pattern}
		\State{output $\langle O_u, T_u\rangle$} \label{code:fc-checking}
		\State break;
	\EndIf \label{code:fc-checking-end}
	\State {$C\leftarrow C';C'\leftarrow \emptyset; \mathrm{level} \gets \mathrm{level}+1$}	
\EndWhile\label{code:level-ends}
\State output $C$ \label{code:output2-end}
\end{algorithmic}
\end{algorithm}

\begin{example}
As shown in Figure~\ref{fig:star_partition}(c), in the bottom level of the lattice structure, candidate $\langle 3,6:3 \rangle $ is pruned because its simplified sequence is empty. Thus, all the object sets containing $\langle 3,6 \rangle $ can be pruned. The remaining two candidates (i.e., $\langle 3,4:1,2,3 \rangle$ and $\langle 3,5:2,3 \rangle$)  derive a new  $\langle 3,4,5:2,3 \rangle$ which is valid. By the forward closure checking, the algorithm can terminate and output $\langle 3,4,5:2,3 \rangle$ as the final closed pattern.
\end{example}

\subsection{Put It Together}
We summarize the workflow of SPARE in Figure~\ref{fig:star_partition} as follows. After the parallel clustering in each snapshot, for ease of presentation, we used an aggregated graph $G_A$ to capture the clustering relationship. However, in the implementation of the map phase, there is no need to create $G_A$ in advance. Instead, we simply need to emit the edges within a star to the same reducer. Before sending stars to reducers, we use a simple best-fit strategy to calculate the star allocation. In best-fit strategy, the most costly unallocated star is assigned to the most empty reducers, where we use the edges in the star as a cost estimation.
 Each reducer is an Apriori Enumerator. When receiving a star $Sr_i$, the reducer creates initial candidate patterns. Specifically, for each $o \in Sr_i$, a candidate pattern $\langle o,i: e(o,i) \rangle$ is created. Then it enumerates all the valid patterns from the candidate patterns. The pseudocode of SPARE is presented in Algorithm~\ref{algo:spm_overview}.

@@

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we prove the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
See Appendix~\ref{apx:spm_correct}.
\end{proof}

### 2016-06-25 sec7_conclusion.tex
Need to add three more experiments
Three more charts

\section{Conclusion and Future Work}
\label{sec:concl}

>>>>

\section{Conclusion}
\label{sec:concl}
In this paper, we present our framework SPARE for detecting General Co-Movement Patterns (GCMP) over large-scale trajectories. Our GCMP is versatile in representing all existing co-movement patterns while being free from the \emph{loose-connection} anomaly. Our SPARE framework, comprising a novel star-partition with several optimization techniques, has shown superior performances and scalability in three real datasets with hundreds of millions trajectories.
